---
title: "week 7 code"
author: "celine"
format: html
execute: 
  warning: false #gets rid of all the warnings
  message: false 
---

#Set up

```{r libraries}
library(tidyverse)
library(here)
library(lterdatasampler)
library(performance)
library(broom)
library(flextable)
library(ggeffects)
library(car)
library(naniar)



```
#linear models
How does stem length predict stem dry mass?
```{r filtering-data}
maples_data <- hbr_maples |>
  filter(year == 2003 & watershed == "Reference")
```

Visualizing missing data

```{r missing-data-vis}
gg_miss_var(maples_data)

```

Create an exploratory data visualization:
```{r explore-data-vis}
ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass)) +
  geom_point()

```
Let's try a model:
```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length, data = maples_data) #lm is to write a formula

maples_model
```


Check assumptions:

1. linear relationship between variables: yes! (used the exploratory data visualization to check that)
2. independence of errors: yes!
3. (making that assumption based on how the data were collected)
4. homoskedasticity of error: yes! (making the decision from residuals vs fitted plot/scale-location plots)
4. normally distributed errors: yes! (looking at QQ plot of residuals)


```{r checking-assumptions} 
par(mfrow= c(2,2))
plot(maples_model)


```


turn off the 2x2 grid:
```{r turning-off-the-grid}
dev.off()

```
























